---
title: "Paper Consumption at ETH Zurich"
subtitle: "Capstone Project"
date: today
author:
  - name: "Ella Haechler"
    orcid: 0009-0007-8251-2702
    email: haella@student.ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: This survey is about the research question on how the consumption of paper changes between Bachelor and Master students at ETH.
license: "CC BY"
citation: 
  container-title: Research Beyond the Lab
  url: https://rbtl-fs25.github.io/website/ # insert website link here
bibliography: bibliography.bib
csl: apa.csl  # other csls https://github.com/citation-style-language/styles
format:
#  docx: default
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    embed-resources: true
#    fig-width: 6  
#    fig-asp: 0.618    # the golden ratio, only adjust fig-asp in chunks where needed
#    fig-align: center
#    out-width: "70%"

# global code chunk options are defined:
execute:
  warning: true
  cache: false   # regularily clear out by knitr::clean_cache()

editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false      #(results shown, code not)
#| message: false   #(prevents message appearance)
#| warning: false   #(prevents warning appearance)

library(tidyverse)
library(ggplot2) #in tidyverse
library(dplyr) #in tidyverse
library(stringr) #in tidyverse
library(readr) #in tidyverse
library(ggthemes)
library(ggridges)
library(readxl)
library(googlesheets4)
library(sf) #standardized way to encode spatial vector data
library(gt) #Presentation-Ready Display Tables
library(gtsummary) #publication-ready analytical and summary tables using the R programming language
library(knitr) #general-purpose tool for dynamic report generation in R using Literate Programming techniques.
library(DT) #Data objects in R can be rendered as HTML tables using the JavaScript library 'DataTables'
library(lubridate) #tools to make dates parsing and manipulation easier

# datasets: ------------------------------------
library(gapminder)
library(palmerpenguins)
library(rnaturalearth)
library(nycflights13)

# data
paper <- read_csv(here::here("data/processed/survey-cleaned-data.csv"))
```

# Introduction

In recent years, sustainability and resource management have gained importance. Large institutions, including universities, are seeking ways to contribute to a more environmentally friendly future and are actively pursuing new strategies for improvement [@2023preferring]. Among the various challenges they face, paper consumption stands out as an area with considerable potential for positive change [@2022longterm].

An anonymous survey examined the paper usage habits of ETH students. The study's goal was to investigate the differences in paper consumption between bachelor and master students at ETH. The analysis of these usage patterns will help to develop future strategies that promote a more responsible use of resources at universities [@henderson2015students].

# Methods

Data for this study was collected through a survey designed using Google Forms, comprising fifteen questions focused on paper consumption habits. The target population included students currently enrolled in bachelor’s or master’s programs at ETH Zurich. The survey link was distributed to fellow students via WhatsApp. Additional participants were recruited in person by approaching students on campus. In total, thirty responses were gathered for analysis. This approach ensured a mix of convenience and random sampling within the ETH student community.

# Results

In the following @tbl-paper-consumption-overview-degree an overview about the basic information collected in the survey is given. Not only did bachelor students consume more paper on average than master students, but their consumption also varied more, as reflected in the higher standard deviation and a significantly higher median. In contrast, master students exhibited both lower average consumption and lower variability. These results suggest that paper consumption tends to decrease and become more constant during the transition from bachelor to master studies.

```{r}
#| label: tbl-paper-consumption-overview-degree
#| tbl-cap: "Printing habits of Bachelor's and Master's students"
#| echo: false #(results shown, code not)

paper |>
  group_by(degree) |>
  summarise(
    Mean = mean(printing_amount, na.rm = TRUE),
    sd = sd(printing_amount, na.rm = TRUE),
    Median = median(printing_amount, na.rm = TRUE),
    Min = min(printing_amount, na.rm = TRUE),
    Max = max(printing_amount, na.rm = TRUE),
    n = n(),
    page_usage_per_person = round(Mean / n, digits = 2)
    ) |>
  ungroup() %>%
  gt() |> 
  fmt_number(columns = c(Mean, sd, Median, Min, Max),
             decimals = 0) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  )

```

@fig-paper-1 displays the distribution of printing locations among bachelor students, with bars representing the count of students for each location, differentiated by their printing decision. The most frequently selected printing location was the university, while other locations such as the copy shop or home were chosen less often. @fig-paper-2 demonstrated the same information for master students. The university is also the most chosen location for printing, where at work is not even displayed and therefore is not a commonly used place to print. The plot also shows the variation in printing decisions (as indicated by the color fill) across different locations. These results provide a clear overview of where bachelor students most commonly print and how their printing decisions vary by location.

Both degree levels most frequently based their printing decision on factors such as convenience or environmental aspects. This pattern suggests that these two considerations significantly influenced the printing behavior of the surveyed population. Cost also plays a role, but is not as significant as expected. It's also interesting to note that bachelor's students print while working, whereas master's students do not. One might expect the opposite, given that master's students have a higher workload than bachelor's students. One reason for this could be that bachelor's students print more pages overall.Further conclusions cannot be drawn due to a lack of information such as explanations for the printing decision none and other.

```{r}
#| label: fig-paper-1
#| fig-cap: "Relationship between printing decisions and location choice of bachelor students"
#| echo: false #(results shown, code not)

ggplot(data = filter(paper, degree == "bachelor"),
       mapping = aes(x = printing_location,
                     fill = printing_decision)) +
  geom_bar() +
  labs(x = "Printing location",
       y = "Count",
       fill = "Printing decision") +
  scale_fill_colorblind()

```

```{r}
#| label: fig-paper-2
#| fig-cap: "Relationship between printing decisions and location choice of master students"
#| echo: false #(results shown, code not)

ggplot(data = filter(paper, degree == "master"),
       mapping = aes(x = printing_location,
                     fill = printing_decision)) +
  geom_bar() +
  labs(x = "Printing location",
       y = "Count",
       fill = "Printing decision") +
  scale_fill_colorblind() +
  coord_cartesian(ylim = c(0, 50))
```

@fig-paper-3 shows the relationship between age and the number of pages printed among engineering students, with data points differentiated by degree level. The graph highlights the variability in print volume between age groups and between undergraduate and graduate students. Master's students, who are also generally older, print fewer documents than undergraduate students. This trend could also be influenced by other factors, such as a reduced number of required courses or changes in the academic workload during the master's program. Among undergraduate students, a trend toward less printing with increasing age is evident. However, no clear linear trend is evident, suggesting that age alone is not a strong predictor of paper consumption in this group.

```{r}
#| label: fig-paper-3
#| fig-cap: "Relationship between age and amount of printed papers"
#| echo: false #(results shown, code not)

ggplot(data = filter(paper, course == "Engineering"),
       mapping = aes(x = age,
                     y = printing_amount,
                     color = degree,
                     shape = degree)) +
  geom_point(size = 5, alpha = 0.7) +
  scale_color_manual(values = c("orange", "lightgreen", "grey")) +
  labs(x = "Age (years)",
       y = "Number of printed sheets",
       color = "Degree",
       shape = "Degree")
```

# Conclusions

-   Survey results show that bachelor students use more paper and display greater variability in their printing habits compared to master students.

```{=html}
<!-- -->
```
-   Paper consumption tends to decrease and become more consistent as students progress from bachelor to master studies, possibly due to changes in academic workload and course requirements.

-   The university is the most common printing location for both groups.

-   Both bachelor’s and master’s students primarily base their printing decisions on convenience and environmental considerations, with cost playing a secondary role.

-   No strong correlation was found between age and paper usage, suggesting that factors other than age, such as degree level and individual preferences, are more influential in determining printing behavior.

-   Further research with a larger and more diverse sample could provide deeper insights into the motivations behind students’ printing decisions and inform more effective sustainability initiatives.

# References
