---
title: "Capstone Project - Paper Consumption Survey"
#subtitle: "Subtitle"
date: today
author:
  - name: "Ella Haechler"
    orcid: 0009-0007-8251-2702
    email: haella@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: This survey is about the research question on how the consumption of paper changes between Bachelor and Master students at ETH.
license: "CC BY"
citation: 
  container-title: Research Beyond the Lab
  url: https://rbtl-fs25.github.io/website/ # insert website link here
bibliography: bibliography.bib
#csl: apa.csl  # other csls https://github.com/citation-style-language/styles
format:
#  docx: default
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    embed-resources: true
#    fig-width: 6  
#    fig-asp: 0.618    # the golden ratio, only adjust fig-asp in chunks where needed
#    fig-align: center
#    out-width: "70%"

# global code chunk options are defined:
execute:
  warning: true
  cache: false   # regularily clear out by knitr::clean_cache()

editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false      #(results shown, code not)
#| message: false   #(prevents message appearance)
#| warning: false   #(prevents warning appearance)

library(tidyverse)
# library(ggplot2) in tidyverse
# library(dplyr) in tidyverse
# library(stringr) in tidyverse
# library(readr) in tidyverse
library(ggthemes)
library(ggridges)
library(readxl)
library(googlesheets4)
library(sf) #standardized way to encode spatial vector data
library(gt) #Presentation-Ready Display Tables
library(gtsummary) #publication-ready analytical and summary tables using the R programming language
library(knitr) #general-purpose tool for dynamic report generation in R using Literate Programming techniques.
library(DT) #Data objects in R can be rendered as HTML tables using the JavaScript library 'DataTables'
library(lubridate) #tools to make dates parsing and manipulation easier

# datasets: ------------------------------------
library(gapminder)
library(palmerpenguins)
library(rnaturalearth)
library(nycflights13)

# data
paper <- read_csv(here::here("data/processed/survey-cleaned-data.csv"))
```

# Introduction

In recent years, sustainability and resource management have gained importance. Large institutions, including universities, are seeking ways to contribute to a more environmentally friendly future and are actively pursuing new strategies for improvement. Among the various challenges they face, paper consumption stands out as an area with considerable potential for positive change.

An anonymous survey examined the paper usage habits of ETH students. The study's goal was to investigate the differences in paper consumption between bachelor and master students at ETH. The analysis of these usage patterns will help to develop future strategies that promote a more responsible use of resources at universities.

# Methods

Data for this study was collected through a survey designed using Google Forms, comprising fifteen questions focused on paper consumption habits. The target population included students currently enrolled in bachelor’s or master’s programs at ETH Zurich. The survey link was distributed to fellow students via WhatsApp. Additional participants were recruited in person by approaching students on campus. In total, thirty responses were gathered for analysis. This approach ensured a mix of convenience and random sampling within the ETH student community.

# Results

In the following @tbl-paper-consumption-overview-degree an overview about the basic information collected in the survey is given.

```{r}
#| label: tbl-paper-consumption-overview-degree
#| tbl-cap: "Printing habits of Bachelor's and Master's students"
#| echo: false #(results shown, code not)

paper |>
  group_by(degree) |>
  summarise(
    Mean = mean(printing_amount, na.rm = TRUE),
    sd = sd(printing_amount, na.rm = TRUE),
    Median = median(printing_amount, na.rm = TRUE),
    Min = min(printing_amount, na.rm = TRUE),
    Max = max(printing_amount, na.rm = TRUE),
    n = n()
  ) |>
  ungroup() %>%
  gt() |> 
  fmt_number(columns = c(Mean, sd, Median, Min, Max),
             decimals = 0) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  )

```

@fig-paper-1 shows ...

```{r}
#| label: fig-paper-1
#| fig-cap: "paper 1"
#| echo: false #(results shown, code not)

ggplot(data = filter(paper, degree == "master"),
       mapping = aes(x = printing_location,
                     fill = printing_decision)) +
  geom_bar() +
  labs(x = "xyz",
       y = "Count",
       fill = "Usage of color") %>%
  scale_fill_colorblind()

```

```{r}
ggplot(data = filter(paper, degree == "bachelor"),
       mapping = aes(x = printing_location,
                     fill = printing_decision)) +
  geom_bar() +
  labs(x = "xyz",
       y = "Count",
       fill = "Usage of color") %>%
  scale_fill_colorblind()
```

In @fig-paper-2 ...

The older, the less people print. Entering master, less printing indeed. but can also have other reason: nnumber of courses, etc.

```{r}
#| label: fig-paper-2
#| fig-cap: "paper 2"
#| echo: false #(results shown, code not)

ggplot(data = filter(paper, course == "Engineering"),
       mapping = aes(x = age,
                     y = printing_amount,
                     color = degree,
                     shape = degree)) +
  geom_point(size = 5, alpha = 0.7) +
  scale_color_manual(values = c("orange", "lightgreen", "grey")) +
  labs(x = "Age (years)",
       y = "Number of printed sheets",
       color = "Degree",
       shape = "Degree")
```

```{r}

ggplot(data = filter(paper, course == "Engineering"),
       mapping = aes(x = lectures_completed,
                     y = printing_amount,
                     color = degree,
                     shape = degree)) +
  geom_point(size = 5, alpha = 0.7) +
  scale_color_manual(values = c("orange", "lightgreen", "grey")) +
  labs(x = "courses",
       y = "Number of printed sheets",
       color = "Degree",
       shape = "Degree")
```

# Conclusions

# References

@2022longterm

@2023preferring

@sopha2013sustainable
